\documentclass[11pt,a4paper,roman]{moderncv}      
\usepackage[english]{babel}



\moderncvstyle{classic}                            
\moderncvcolor{green}                            

% character encoding
\usepackage[utf8]{inputenc}                     

% adjust the page margins
\usepackage[scale=0.75]{geometry}

% personal data
\name{Krishna Vijay}{Samayamantri}


\phone[mobile]{+1 (702) 722-4071}               
\email{svrbasky@gmail.com}                             


\begin{document}

\recipient{To}{Recruiter, \\ Birmingham and Women's Hospital}
\date{\today}
\opening{Hi!}
\closing{Thanks in advance!}
\enclosure[Attachment]{CV}
\makelettertitle


% The first paragraph of your job application letter should include information on why you are writing. Mention the job you are applying for and where you found the position. If you have a contact at the company, mention the person's name and your connection here.
I am Krishna Vijay. I recently graduated from Cal State LA with Master's in Electrical Engineering with specialization in Biomedical Engineering. I found the job advertisement,"Research Associate at Brigham and Women's Hospital" on Indeed.com and thought I would be a good fit for it.

% The next section of your cover letter should describe what you have to offer the company. Make strong connections between your abilities and the requirements listed in the job posting. Mention specifically how your skills and experience match the job. Expand on the information in your resume, don't just repeat it.
% Try to support each statement you make with a piece of evidence. Use several shorter paragraphs or bullets rather than one large block of text, which can be difficult to read and absorb quickly.

You are looking for someone with research capabilities in medical imaging and data visualization, programming skills and academic writing. I have worked on various research and development projects in biomedical engineering since 2012. I have worked in diagnostics using biomedical signals such as, ECG, EEG and EMG. I have built a prototype medical imaging device for the LA Biohack Hackathon, called Automated IR Imaging of Broken Bones (AIRiBnB) which performs triage to detect and categorize injuries based on inflammation. My team got 3rd prize for this project. 
For my Master's thesis, I built a brain machine interface algorithm that detects whether subject has performed a left-hand or right-hand reach, based on their EEG and an SVM classifier.
In 2013, I have built India's first mind-controlled wheelchair using the Emotiv BCI device and an electric wheelchair. In the same year, I published an IEEE paper, where patient ECG can be sorted into arrhythmic and normal ECG. Furthermore, we found out that each patient's ECG is unique and that can be used as a bio-metric identifier. 

I have also tried to build my own startup in online learning and home automation. After building prototypes, I failed to launch it in market.


% Conclude your application letter by thanking the employer for considering you for the position. Include information on how you will follow-up. State that you will do so and indicate when (one week's time is typical). You may want to reduce the time between sending out your resume and follow up if you fax or email it.
As a lifelong learner and an entrepreneur, I am able to consider all the possible scenarios and tailor my approach towards the best results. This would make me a valuable addition to your company. Please find my application and resume attached. 
I look forward to hearing from you.

\vspace{0.5cm}


\makeletterclosing

\end{document}
